POMDP comparisons across sigma_m, sigma_g

### 2018-01-06 appendix/appendixB.Rmd
updated figures under appendix B

```{r eval=TRUE}
dir.create(log_dir)
options(mc.cores = 1)

@@

```{r}
meta <- meta_from_log(data.frame(model="gs"), log_dir)  %>% 
  left_join(
    ## use the estimated sigma_m, r, K pars recorded in the logged meta.csv.  Technically
    ## these should be the same as the above, but without random seed re-running the nimble
    ## code but not re-running these can create mis-matches.  
    select(meta, sigma_m, commonname, scenario),   
    by = c("sigma_m", "commonname")) %>% 
  arrange(scenario)
alphas <- alphas_from_log(meta, log_dir)
#models <- models_from_log(meta)
```

@@

```{r}
pomdp_sims <- 
  pmap_dfr(list(models, alphas, 1:dim(meta)[[1]]), 
           function(.x, .y, .z){

>>>>

```{r eval=FALSE}
dir.create(log_dir)
options(mc.cores = 1)

@@

```{r message=FALSE}
meta <- meta_from_log(data.frame(model="gs"), log_dir)  %>% 
  mutate(scenario = as.character(scenario)) %>%
  left_join(
    ## use the estimated sigma_m, r, K pars recorded in the logged meta.csv.  Technically
    ## these should be the same as the above, but without random seed re-running the nimble
    ## code but not re-running these can create mis-matches.  
    select(meta, sigma_m, commonname, scenario),   
    by = c("scenario", "sigma_m", "commonname")) %>% 
  arrange(scenario)
alphas <- alphas_from_log(meta, log_dir)
#models <- models_from_log(meta)
```

@@

```{r}
set.seed(123456)
pomdp_sims <- 
  pmap_dfr(list(models, alphas, 1:dim(meta)[[1]]), 
           function(.x, .y, .z){
